---
title: "Analysis and Visulization of Infert Dataset"
author: "Gajanan Mirkhale"
date: "January 16, 2017"
output:
  pdf_document: default
  word_document: default
---
###Infert Dataset Description
---
#Description

This is a matched case-control study dating from before the availability of conditional logistic regression.
Usage

#infert

###Format
1. 	Education 	          0 = 0-5 years
		                      1 = 6-11 years
		                      2 = 12+ years
2. 	age 	age in years of case
3. 	parity 	count
4. 	number of prior 	    0 = 0
	induced abortions 	    1 = 1
		                      2 = 2 or more
5. 	case status      	    1 = case
		                      0 = control
6. 	number of prior 	    0 = 0
	spontaneous abortions 	1 = 1
		                      2 = 2 or more
7. 	matched set number 	  1-83
8. 	stratum number      	1-63
---

```{r setup, include=FALSE}
library(ggplot2)
library(reshape2)
library(plotly)
library(MASS) 
library(caret)
head(infert)
data("infert")
names(infert) 
ls.str(infert)                  #Overview of the data

summary(infert)                 #summary of the dta
table(infert$case)


#Checking out the missing values
sapply(infert, function(x) sum(is.na(x))) #No missing values 
```

##create a missing map

```{r}
# load libraries
library(Amelia)
library(mlbench)

missmap(infert, col=c("black", "grey"), legend=FALSE) # No missing values in missing map
```

## pair-wise scatterplots of all attributes

```{r}
pairs(infert)

```

## pair-wise Scatterplot Matrix By Class

```{r}
pairs(education~., data = infert, col=infert$education)
```

## combine multiple plots into one overall graph

```{r}
par(mfrow=c(2,2),
plot(infert$pooled.stratum),
plot(infert$parity),
plot(infert$age),
plot(table(infert$parity)))
dev.off()
```

## Create a Histogram 

```{r}
hist(infert$age,col ="blue")
```

#generate a linear regression model of the two variables

```{r}
spontaneous = infert$spontaneous
age = infert$age
stratum = infert$stratum

plot( stratum, age )
abline(lm( age ~ stratum))
```

##analysed by conditional logistic regression

```{r}
 require(stats)
model1 <- glm(case ~ spontaneous+induced, data = infert, family = binomial())
summary(model1)
model1


library(survival)
 data(infert)
model2 <- glm(case ~ age+parity+education+spontaneous+induced,
                               data = infert, family = binomial())
summary(model2)
```

##Comparison of two logistic regression models

```{r}

library('epiDisplay')

model1 <- glm(case ~ induced + spontaneous, data=infert, family=binomial)
logistic.display(model1)


# This is actually not a causal relationship
layout(matrix(1, ncol = 1))
lroc(model1, title=TRUE, auc.coords=c(.5,.1))


lroc(model1, title=TRUE, cex.main=2, cex.lab=1.5, col.lab="blue", cex.axis=1.3, lwd=3)
lroc1 <- lroc(model1) # The main title and auc text have disappeared

model2 <- glm(case ~ spontaneous, data=infert, family=binomial)
logistic.display(model2)

lroc2 <- lroc(model2, add=TRUE, line.col="brown", lty=2)
legend("bottomright",legend=c(lroc1$model.description, lroc2$model.description),
       lty=1:2, col=c("red","brown"), bg="white")
title(main="Comparison of two logistic regression models")
lrtest(model1, model2) 

```

